Heuristics are proceeded during the algorithm in order to speed-up the resolution time by finding feasible solutions allowing to cut more branches.

\subsection{Root heuristics}
\label{heuristic-root}

A first heuristic can be processed at root. This is a very important if we want to have a fast algorithm because the higher a branch is cut, the less node are explored. If a very good bound is found at the root, it can prevent to explore a huge part of the tree.

The three heuristics which can be used at root are three variations of a more general heuristic called \textit{Decreasing Order Heuristic} \cite{johnson1973near}. The key idea is to sort the items is decreasing order and for each item, choose a bin to pack it. The heuristics differs on the way to choose the bin. The general Decreasing Order Heuristic can be summarized as following :

\begin{figure}[!ht]
	\centering
	\begin{minipage}{0.5\linewidth}
		\begin{algorithm}[H]
			\DontPrintSemicolon 
			\SetAlgoLined
			\While{The are items that have not been packed}{
				Pick the item with the largest size\;
				\If{The item can't be packed in any bin}{Add a new bin}
				Choose a bin able to pack the item\;
				Put the item in the bin\;
			}
			\caption{Decreasing Order Heuristic}
		\end{algorithm}
	\end{minipage}
\end{figure}

The three heuristics implemented are the \textit{First-Fit-Decreasing} (FFD), the \textit{Best-Fit-Decreasing} (BFD) and the \textit{Worst-Fit-Decreasing} (WFD) and they select the bin to pack the item as following :
\begin{itemize}
	\item \textbf{FFD} :  Chooses the first bin in which the item can be packed
	\item \textbf{BFD} :  Chooses the bin with the least amount of free space in which the item can be packed
	\item \textbf{WFD} : Chooses the bin with the most amount of free space in which the item can be packed
\end{itemize}
As all these heuristics have to sort the items (complexity in $\Oc( N\log N)$) and to proceed a loop over each item (complexity in $\Oc (N)$), their overall complexity is $\Oc (N\log N)$. Furthermore, if $\opt{B}$ is the optimal number of bins, it was shown that the results in the worst case for these heuristics are
\begin{itemize}
	\item \textbf{FFD} :  $\floor{1.7 \opt{B}}$ \cite{dosa2013first}
	\item \textbf{BFD} : $\floor{1.7 \opt{B}}$ \cite{dosa2014optimal}
	\item \textbf{WFD} : $2\opt{B} - 2$ \cite{johnson1973near}
\end{itemize}
We can see that these heuristics are very interesting both regarding to their complexity and their efficiency. It is very recommended to enable it when running the BnP algorithm.